---
title: "Developing Data Products Week 4 Assignment"
author: "Jeffrey Waitkevich"
date: "February 22, 2020"
output: ioslides_presentation
---

## Reproducible Pitch

For the week four peer graded assignment of the Developing Data Science Coursera class, I decided to make an interactive webpage that creates histograms based on the per game averages of the three most popular statistics in baskebtall from the 2018-19 NBA Season. The app can be found at https://jwaitkevich.shinyapps.io/NBA-Per-Game-Stats-2018-19/. The code for the app can be found at https://github.com/jwaitkevich/Developing-Data-Products-Week-4-Assignment. 

## Inputting the Data
```{r, message = FALSE}
library(rvest)
library(dplyr)
url <- "https://www.basketball-reference.com/leagues/NBA_2019_per_game.html"
nba.ref <- read_html(url)
nba.ds <- nba.ref %>%
    html_nodes(xpath='//*[@id="per_game_stats"]') %>%
    html_table(fill = TRUE)
nba.totals <- nba.ds[[1]]
clean.nba.totals <- subset(nba.totals, Rk != "Rk",
                           select = c("Rk", "Player", "Tm",
                                      "TRB", "AST", "PTS"))
clean.nba.totals$Rk <- as.numeric(unlist(clean.nba.totals$Rk))
clean.nba.totals$PTS <- as.numeric(clean.nba.totals$PTS)
clean.nba.totals$TRB <- as.numeric(clean.nba.totals$TRB)
clean.nba.totals$AST <- as.numeric(clean.nba.totals$AST)
points <- clean.nba.totals[,c(1,6)]
assists <- clean.nba.totals[,c(1,5)]
rebounds <- clean.nba.totals[,c(1,4)]
```

## A Look at the Dataset
We can see that the dataset lists the player alphabetically and include the three stats we use in our histograms.
```{r}
head(clean.nba.totals, 12)
```
## An Example of the Output
```{r}
hist(points[,2], breaks = 10, col = "red", border = "blue", 
     xlab = "Per Game Average", 
     main = "Histogram of Selected Stat")
```

